\begin{Song}{Fuck you}{Cee Lo Green}
\begin{multicols}{2}

\begin{Chorus}
I see you driving 'round town
With the girl I love
And I'm like "Fuck you!"
\backup{Ooo, ooo, ooh}
\espaceInterStrophe

I guess the change in my pocket
Wasn't enough
I'm like "Fuck you!
And fuck her too."
\espaceInterStrophe

I said "If I was richer,
I'd still be with ya"
Ha, now ain't that some shit?
\backup{Ain't that some shit}
\espaceInterStrophe

And although there's pain in my chest
I still wish you the best
With a\dots\ "Fuck you!"
\backup{Ooo, ooo, ooh}
\end{Chorus}
\espaceInterStrophe

\begin{Verse}
Yeah I'm sorry, I can't afford a Ferrari
But that don't mean I can't get you there
I guess he's an XboX, and I'm more Atari
But the way you play your game ain't fair
\end{Verse}
\espaceInterStrophe

\begin{PreChorus}
I pity the fool
That falls in love with you
\backup{Oh shit she's a golddigger}
Well
\backup{Just thought you should know nigga}
Oooooooooh
I've got some news for you
\espaceInterStrophe

Yeah go run and tell your little boyfriend
\end{PreChorus}
\espaceInterStrophe

\tochorus
\espaceInterStrophe

\begin{Verse}
Now I know, that I had to borrow
Beg and steal and lie and cheat
Trying to keep ya, trying to please ya
Cause bein' in love with your ass ain't cheap
\end{Verse}
\espaceInterStrophe

\direction{Pre-Chorus}
\espaceInterStrophe

Ooh I really hate your ass right now
\espaceInterStrophe

\tochorus
\espaceInterStrophe

\begin{Bridge}
Now baby, baby, baby
Why d'you wanna, wanna hurt me so bad
\backup{So bad, so bad, so bad}
I tried to tell my mamma
But she told me "This is one for your dad."
\backup{Your dad, your dad, your dad}
Uh! Why? Uh! Why? Uh! Why lady?
Oh! I love you! Oh I still love you!
\end{Bridge}
\espaceInterStrophe

\tochorus
\espaceInterStrophe

\end{multicols}

\vfill

\begin{Chords}[Verse/Chorus]
\hline
C & D\sept & F & C\\\hline
\end{Chords}
\espaceInterGrille

\begin{Chords}[Bridge]
\hline
E\mineur & A\mineur & D\mineur & D\mineur\\\hline
\slashbox{E\mineur}{E} & \slashbox[0pt][r]{A\mineur\ B\mineur}{C C\diese} & D & D\mineur\\\hline
D & F & D & \slashbox[0pt][r]{A\mineur\ B\mineur}{C C\diese}\\\hline
D & F & G & G\\\hline
\end{Chords}

\vfill

\end{Song}

% ==============================================================================

