\begin{Song}{Rebel Rebel}{David Bowie}
\begin{multicols}{2}

\begin{Verse}
You've got your mother in a whirl
She's not sure if you're a boy or a girl
Hey babe, your hair's alright
Hey babe, let's go out tonight
\espaceInterStrophe

You like me, and I like it all
We like dancing and we look divine
You love bands when they're playing hard
You want more and you want it fast
\end{Verse}
\espaceInterStrophe

\begin{PreChorus}
They put you down, they say I'm wrong
You tacky thing, you put them on
\end{PreChorus}
\espaceInterStrophe

\begin{Chorus}
Rebel Rebel, you've torn your dress
Rebel Rebel, your face is a mess
Rebel Rebel, how could they know?
Hot tramp, I love you so!

Don't ya?
\end{Chorus}
\espaceInterStrophe

\indication{Repeat first verses}
\espaceInterStrophe

\tochorus[x2]
\columnbreak

\begin{Verse}
You've torn your dress, your face is a mess
You can't get enough, but enough ain't the test
You've got your transmission and your live wire
You got your cue line and a handful of ludes
You wanna be there when they count up the dudes
\espaceInterStrophe

And I love your dress
You're a juvenile success
Because your face is a mess
So how could they know?
I said, how could they know?
\espaceInterStrophe

So what you wanna know Calamity's child,
Where'd you wanna go?
What can I do for you? Looks like you've been there too
'Cause you've torn your dress
And your face is a mess
Ooo, your face is a mess
Ooo, ooo, so how could they know?
Eh, eh, how could they know?
\end{Verse}
\espaceInterStrophe

\vfill
~
\end{multicols}

\vfill

\begin{multicols}{2}

\gridGroupNormal

\begin{Chords}[Verse/Chorus]
\hline
\\\hline
\end{Chords}
\espaceInterGrille

\gridGroupCapoAndBetter{3}{1}

\begin{Chords}[Verse/Chorus]
\hline
\\\hline
\end{Chords}

\end{multicols}

\vfill

\end{Song}



