\begin{Song}{Hero}{Enrique Iglesias}
\begin{multicols}{2}
\begin{Verse}
Let me be your hero
\espaceInterStrophe

Would you dance if I asked you to dance?
Would you run and never look back?
Would you cry if you saw me crying?
And would you save my soul, tonight?
\espaceInterStrophe


Would you tremble if I touched your lips?
Would you laugh? Oh please tell me this
Now would you die for the one you loved?
Hold me in your arms, tonight
\end{Verse}
\espaceInterStrophe

\begin{Chorus}
I can be your hero, baby
I can kiss away the pain
I will stand by you forever
You can take my breath away
\end{Chorus}
\vfill
\columnbreak

\begin{Verse}
Would you swear that you'll always be mine?
Or would you lie? Would you run and hide?
Am I in too deep? Have I lost my mind?
I don't care, you're here tonight
\end{Verse}
\espaceInterStrophe

\tochorus
\espaceInterStrophe

\begin{Verse}
Oh, I just want to hold you
I just want to hold you, oh, yeah
Am I in too deep? Have I lost my mind?
Well, I don't care, you're here tonight
\end{Verse}
\espaceInterStrophe

\tochorus
\espaceInterStrophe

\begin{Chorus}
I can be your hero
I can kiss away the pain
And I will stand by you forever
You can take my breath away
You can take my breath away

I can be your hero
\end{Chorus}
\end{multicols}

\vfill

\begin{Chords}[Verse]
\hline
G      & G      & E\mineur\sept & E\mineur\sept\\\hline
C\add9 & C\add9 & D\sus4        & D\sus4\\\hline
G      & G      & E\mineur\sept & E\mineur\sept\\\hline
C\add9 & D\sus4 & G             & G\\\hline
\end{Chords}
\espaceInterGrille

\begin{Chords}[Chorus]
\hline
G & D & C & C(\add9)\\\hline
\end{Chords}

\vfill

\end{Song}

% ==============================================================================

