\begin{Song}{Locked Away}{R. City ft. Adam Levine}
\begin{multicols}{2}

\begin{Chorus}
If I got locked away
And we lost it all today...
Tell me honestly...
Would you still love me the same?
If I showed you my flaws
If I couldn't be strong
Tell me honestly
Would you still love me the same?
\end{Chorus}
\espaceInterStrophe

\begin{Verse}
Right about now...
If a judge for life me...
Would you stay by my side?
Or is ya gonna say good-bye?
Can you tell me right now?
If I couldn't buy you the fancy things in life
Shawty, would it be alright
Come and show me that you are down (ah-ha)
\end{Verse}
\espaceInterStrophe

\begin{PreChorus}
Now tell me would you really ride for me?
\backup{would you really ride for me?}
Baby, tell me would you die for me?
\backup{tell me would you die for me?}
Would you spend your whole life with me?
\backup{what's up?}
Would you be there to always hold me down?

Tell me would you really cry for me?
\backup{would you really cry for me?}
Baby, don't lie to me
\backup{baby, don't lie to me}
If I didn't have anything...
\backup{what's up?}
I wanna know would you stick around?
\end{PreChorus}
\espaceInterStrophe

\tochorus
\espaceInterStrophe

\begin{Verse}
Skiddly-dong-dong-dong dang
All I want is somebody real who don't need much
A gal I know that I can trust...
To be here when money low
If I did not have nothing else to give but love...
Would that even be enough?
Gal, meh need fi know (ah-ha)
\end{Verse}
\espaceInterStrophe

\indication{PreChorus}
\espaceInterStrophe

\tochorus
\espaceInterStrophe

\begin{Bridge}
Tell me, tell me, would you want me? (want me)
Tell me, tell me, would you call me? (call me)
If you knew I wasn't ballin'
'Cause I need a gal who's always by my side...
Tell me, tell me, do you need me? (need me)
Tell me, tell me, do you love me yea?
Or is ya just tryna play me?
'Cause I need a gal to hold me down for life...
\end{Bridge}
\espaceInterStrophe

\tochorus[x2]

\begin{Chorus}
Would you still love me the same?
\end{Chorus}
\espaceInterStrophe

\end{multicols}

\vfill

\begin{multicols}{2}

\gridGroupNormal

\begin{Chords}[Verse]
\hline
B\bemol\mineur & F\diese & C\diese & G\diese\\\hline
\end{Chords}
\espaceInterGrille

\begin{Chords}[PreChorus/Chorus]
\hline
C\diese & B\bemol\mineur & F\diese & \slashbox{C\diese}{G\diese}\\\hline
\end{Chords}

\gridGroupCapoAndBetter{1}{0}

\begin{Chords}[Verse]
\hline
A\mineur & F & C & G\\\hline
\end{Chords}
\espaceInterGrille

\begin{Chords}[PreChorus/Chorus]
\hline
C & A\mineur & F & \slashbox{C}{G}\\\hline
\end{Chords}

\end{multicols}

\vfill

\end{Song}

% ==============================================================================
